Approximation as Differentiation

### 2025-06-09 main/first-order.tex
LatGal as a CMon-category.

$\LatGal$ also has biproducts. The projections $\pi_1$ and $\pi_2$ from the product lattice $X \times Y$ have
both upper and lower adjoints; this means that $X \times Y$, which we shall hereafter write as $X \biprod Y$,
is both a product and a coproduct, with projections $\biproj_X$ and $\biproj_Y$ and injections $\biinj_X$ and
$\biinj_Y$ given by:

\vspace{-4mm}
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{align*}
   \biproj_X = \prodM{\id_X}{\bot_Y} \adj \proj_1: X \biprod Y \to X \\
   \biproj_Y = \prodM{\bot_X}{\id_Y} \adj \proj_2: X \biprod Y \to Y
\end{align*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{align*}
   \biinj_X = \pi_1 \adj \prodM{\id_X}{\top_Y} : X \to X \biprod Y \\
   \biinj_Y = \pi_2 \adj \prodM{\top_X}{\id_Y}: Y \to X \biprod Y
\end{align*}
\end{center}
\end{minipage}
\vspace{2mm}

\noindent The trivial 1-point lattice, which is both terminal and initial and we write as $0$, is the unit for
$\biprod$.

>>>>

$\LatGal$ also has biproducts. The projections $\pi_1$ and $\pi_2$ from the product lattice $X \times Y$ have
both upper and lower adjoints; this means that $X \times Y$ (which we shall write as $X \biprod Y$), is both a
product and a coproduct, with projections $\biproj_X$ and $\biproj_Y$ and injections $\biinj_X$ and $\biinj_Y$
given by:

\vspace{-4mm}
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{align*}
   \biproj_X = \prodM{\id}{\bot} \adj \proj_1: X \biprod Y \to X \\
   \biproj_Y = \prodM{\bot}{\id} \adj \proj_2: X \biprod Y \to Y
\end{align*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{align*}
   \biinj_X = \pi_1 \adj \prodM{\id}{\top} : X \to X \biprod Y \\
   \biinj_Y = \pi_2 \adj \prodM{\top}{\id}: Y \to X \biprod Y
\end{align*}
\end{center}
\end{minipage}
\vspace{2mm}

\noindent with the trivial 1-point lattice as a zero object (terminal and initial).
